A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)

### 2018-04-13 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

The BaseCase permeability model used here retains the checkerboard desgined used by the recently named authors. Albeit, the permeability data for each block in the set of diagonally opposite blocks have similar value (\ie not exactly the same as in the papers referred to), although one set can still be referred to as a set of high permeability blocks while the other set is referred to as a set of low permeability blocks. Furthermore, within each block, the permeability field varies within a pre-defined range and consists of $1600$ permeability values. More details on the design of the permeability field for the BaseCase is available in section~\ref{subsubsection:basecase_preprocess_algorithm}. Figures~\ref{fig:PermFields}a and~\ref{fig:PermFields}b give a pictorial representation of the permeability field for the base case with the mesh discretization visible and invisible, respectively. Using the labelling scheme used by \citet{dawe_2008}, the quadrant model block $K1,~K2,~K3$ and $K4$ are top left, bottom left, top right and bottom right respectively.

As already mentioned, four upscaled permeability field models were obtained from the high-resolution ({\it i.e.} the BaseCase) permeability field. When compared to the BaseCase model, all the upscaled models were upgridded to reduce the resolution of the permeability field (Fig.~\ref{fig:HiRes_LowRes_Mesh}). The first two upscaled models are referred to as the ArithMean and the HarmMean Cases, and this is because they are based on the arithmetic and the harmonic averaging methods, respectively. In both the ArithMean and HarmMean Cases, averages are calculated for each block using the $1600$ data points from the blocks of the BaseCase to obtain a permeability value for each block in the upscaled models. This effectively homogenizes the permeability field in each block. The upscaled permeability field for the third and fourth cases are referred to as PDFCase and SVDCase, respectively. And, as can be deduced from the names, these cases are based on probability density function (PDF) and singular value decomposition (SVD). The description for these permeability field models are more involved and are presented in section ~\ref{subsubsection:pdfcase_preprocess_algorithm} and ~\ref{subsubsection:svdcase_preprocess_algorithm} respectively. It is appropriate to note that although these models (PDFCase and SVDCase) are upscaled, they retain heterogeneity within the blocks.

>>>>

The BaseCase permeability model used here retains the checkerboard desgined used by the recently named authors. Albeit, the permeability data for each block in the set of diagonally opposite blocks have similar value (\ie not exactly the same as in the papers referred to), although one set can still be referred to as a set of high permeability blocks while the other set is referred to as a set of low permeability blocks. Furthermore, within each block, the permeability field varies within a pre-defined range and consists of $1600$ permeability values. More details on the design of the permeability field for the BaseCase is available in section~\ref{subsubsection:basecase_preprocess_algorithm}. Figures~\ref{fig:PermFields}a and~\ref{fig:PermFields}b give a pictorial representation of the permeability field for the base case with the mesh discretization visible and invisible, respectively.  Using the labelling scheme used by \citet{dawe_2008}, the quadrant model block $K1,~K2,~K3$ and $K4$ are top left, bottom left, top right and bottom right, respectively.

As already mentioned, four upscaled permeability field models were obtained from the high-resolution (\ie the BaseCase) permeability field. When compared to the BaseCase model, all the upscaled models were upgridded to reduce the resolution of the permeability field (Fig.~\ref{fig:HiRes_LowRes_Mesh}). The first two upscaled models are arithmetic and harmonic averaging methods  (referred to as ArithMean and HarmMean, respectively).

In both sets of test-cases, averages are calculated for each block using the $1600$ data points from the blocks of the BaseCase to obtain a permeability value for each block in the upscaled models. This effectively homogenizes the permeability field in each block. The upscaled permeability field for the third and fourth cases are referred to as PDFCase and SVDCase, respectively. And, as can be deduced from the names, these cases are based on probability density function (PDF) and singular value decomposition (SVD). The description for these permeability field models are more involved and are presented in section ~\ref{subsubsection:pdfcase_preprocess_algorithm} and ~\ref{subsubsection:svdcase_preprocess_algorithm} respectively. It is appropriate to note that although these models (PDFCase and SVDCase) are upscaled, they retain heterogeneity within the blocks.

### 2018-04-13 Papers/AppliedMaths2018/article_figure1.tex
updates

\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\hbox{\includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_MeshOnly.png}
      \includegraphics[width=.56\textwidth]{./Pics/ArithMeanCase/ArithMeanCase_MeshOnly.png}}
\vspace{0.cm}
\hbox{\hspace{0.25cm} (a) High Resolution Grid(BaseCase) \hspace{0.75cm} (b) Low Resolution Grid(Upscaled Cases) \hspace{3.0cm}}
\vspace{0.5cm}
}   
\caption{Simulation grid for the high resolution case and the upscaled cases}
\label{fig:HiRes_LowRes_Mesh}
\end{figure}

>>>>

\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\hbox{\includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_MeshOnly.png}
      \includegraphics[width=.56\textwidth]{./Pics/ArithMeanCase/ArithMeanCase_MeshOnly.png}}
\vspace{0.cm}
\hbox{\hspace{0.25cm} (a) High Resolution Grid (BaseCase) \hspace{0.75cm} (b) Low Resolution Grid (Upscaled Cases) \hspace{3.0cm}}
\vspace{0.5cm}
}   
\caption{Mesh grid used in the performed numerical simulations: (a) high-resolution and (b) upscaled cases. \red{(ADD NUMEBR OF ELEMENTS OR NODES FOR EACH CASE)}}
\label{fig:HiRes_LowRes_Mesh}
\end{figure}
